### 2024-03-23 tesis_Ashish/Chapter1/chapter1.tex
Update 23 Mar

>>>>

\begin{table}[h]
  \centering
  \caption[Precision for Run1 and Run2]{Summary of center of mass energy, integrated luminosity, and systematic uncertainty per year during the CMS pPb and PbPb luminosity measurement \cite{CMS-PAS-LUM-13-002} \cite{CMS-PAS-LUM-17-002} \cite{CMS-PAS-LUM-18-001}.}
\begin{tabular}{c c c c}
  Year & Center of Mass Energy/nucleon & Systematic Uncertainty \\
  & (TeV) & (\%) \\
\hline
2013 & 2.76 & 3.4(3.6)  \\
2016 &  5.02  & 3.2(3.7)\\
2018 & 5.02 & 1.5 \\
\end{tabular}
\label{tab:lumi}
\end{table}
